### 2020-06-19 README.Rmd
README update

<!-- badges: end -->

@@

* Currently `code_nuts1()` and `code_nuts2()` is implemented but this will be replaced with a more comprehensive NUTS0-NUTS3 level helper function to make the regional coding consistent.

>>>>

[![Travis build status](https://travis-ci.com/antaldaniel/eurobarometer.svg?branch=master)](https://travis-ci.com/antaldaniel/eurobarometer)
<!-- badges: end -->

@@

* Currently `code_nuts1()` and `code_nuts2()` is implemented but this will be replaced with a more comprehensive `NUTS0`-`NUTS3` level helper function to make the regional coding consistent.
